On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-05-28 documents/paper.tex
SPICE

\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{blindtext,graphicx}
\usepackage[absolute]{textpos}
\usepackage[parfill]{parskip}
\usepackage[colorlinks]{hyperref}

@@

@@

Chiefly among the enablers are of course my parents, without which the author would not have existed[] - but who also supported this work financially.

@@

{\Large Captain's Log, Supplemental}

@@

\paragraph{Lessons Learned}

@@

When iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs) of each distinct test. Including a picture with a webcam of the assembled board is also helpful.

@@

@@

\end{document}

>>>>

\usepackage{multicol}
\usepackage{fancyhdr}
\usepackage{blindtext,graphicx}
\usepackage[absolute]{textpos}
\usepackage[parfill]{parskip}
\usepackage[colorlinks]{hyperref}
\usepackage{hyperref}

@@

\footnote{footnotes working fine}

{\it "You cannot create a VCO that way. It is not easy."}
{ - An anonymous admirer.}

@@

Chiefly among the enablers are of course my parents, Doris and Brian, without which this work would have been done by someone else[] - but who also supported this work financially.

@@

{\Large Captain's Log, Supplemental}\\

[Steenput 1999] has an interesting analytic method to synthesize a SPICE model suitable for a transient simulations from S-parameter measurements using negative resistances.

However, it seems to neglect the I/V characteristic, so we synthesized the SPICE model using an optimization method [Polyfet 1998].

OpenEMS is excellent, with Python bindings, lumped . However, embarassingly, we were not able to resolve all the dependency issues in order to install it.

\label{para}
\ref{para}

@@

\paragraph{Lessons Learned} \

\rule{\linewidth}{0.2pt}

@@

This is obvious to all compentent, but when rapidly iteratively testing with simulations, it may be helpful to automatically save a package with images of all the components (schematics, graphs) of each distinct test. Including a picture with a webcam of the assembled board is also helpful.

@@

\rule{\linewidth}{0.2pt}

A great deal of time was spent trying to resolve version conflicts and dependency hells with the numerous libraries used by all the simulation programs. This also wastes developer time - some fraction of issues raised are due to library version conflicts. OpenFOAM's Docker installation is excellent.

Running chroot with the original developer's Linux distribution is also of some utility, but clunky.

Packaged binaries help this slightly, but of course don't help if modifications are required, and managing shared libraries is still a tricky matter.

In some situations (especially where the library has a permissive licence) it could be useful to consider packaging a complete, batteries-included 'known good' repository, either with the source of all the correct library versions included, or with a script to clone and compile the specific version used, and integrating all the libraries with the build system.

For instance, this was done with the PDB reader.

\rule{\linewidth}{0.2pt}

@@

\Acrobatmenu{GoBack}{Back}
\end{document}
